% learn about REVTeX at https://journals.aps.org/revtex
% useful references:
%   https://cdn.journals.aps.org/files/revtex/summary4-1.pdf
%   ftp://ftp.dante.de/tex-archive/info/latex-refsheet/LaTeX_RefSheet.pdf
%   http://www-groups.mcs.st-andrews.ac.uk/~alanc/pub/c_tikzref/c_tikzref.pdf
\documentclass[
%draft,
aps,prd,
preprint,
onecolumn,
12pt,
amsmath, amssymb,
secnumarabic,
]{revtex4-1}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage[dvipsnames]{xcolor}
\usepackage{standalone}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{minted}
\usepackage{siunitx}
\usepackage[italicdiff]{physics}

\hypersetup{%
colorlinks=true,
linkcolor=RoyalBlue,
urlcolor=RoyalBlue,
citecolor=RoyalBlue,
}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{calc}
\graphicspath{{../png/}}
\usemintedstyle{vs}
\definecolor{LightGray}{gray}{.9}
\setminted[python]{%
bgcolor=LightGray,
mathescape=true,
python3=true,
baselinestretch=1,
}

\newcommand{\comment}[1]{}
\newcommand{\python}[1]{\textcolor{BrickRed}{\texttt{#1}}}

\begin{document}

\title{Gravispy: gravitational simulations in open source software}
\homepage{https://github.com/cjayross/gravispy}
\author{Spence Norwood}
\author{Kellen O'Keefe}
\author{Calvin Ross}
\affiliation{University of Texas at Dallas, Physics Department}
\begin{abstract}
Gravispy is designed to visualize the effects of gravitational lensing.
The goals of the project is to calculate a massive object's effect on spacetime using the Schwarzschild metric and modeling the resulting warped perspective in three dimensions.
By using the Gauss-Kronrod quadrature formula for integration and the Brent-Dekker method for finding the roots of equations, the null-geodesics representing the trajectories of light are calculated numerically at radii near the event horizon of a black hole.
These values are then used to create a mapping between the light of the unperturbed state supplied by the user and the final lensed state.
With this map, a resultant image is produced and is projected onto a sphere using OpenGL to provide a panoramic view of the environment.
The results of this project have been generally successful.
Gravitational lensing has been correctly modeled---with the exception of a small shearing of the output image---and the lensing effect is viewable in a three dimensional model as intended.
Initial goals were to make the simulation dynamic, but currently only a static simulation is supported.
Future improvements to this project could be made by implementing this functionality, and by increasing the physical accuracy of the simulation by modeling the effect of blueshift and the existence of hidden images.
\end{abstract}
\maketitle

\section{Introduction\label{sec:intro}}
\input{1_intro}

\section{Motivation\label{sec:motive}}
\input{2_motive}

\section{Methods\label{sec:method}}
\input{3_method}

\section{Results\label{sec:results}}
\input{4_results}

\section{Discussion and Conclusion}
\input{5_remarks}

\nocite{*}
\bibliography{report}

\end{document}
